---
title: "Qanon Analysis"
author: Ross Dahlke
affiliation: Stanford University
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = F,
	message = FALSE,
	warning = FALSE
)
options(scipen = 99999)
library(nnet)
library(tidyverse)
```


```{r}
qanon_by_person <- read_csv("data/qanon_by_person.csv")
```


# Exposure

## Percent exposed

```{r}
tibble(mean = diagis::weighted_mean(x = qanon_by_person %>% pull(q_exposure_flag),
     w = qanon_by_person %>% pull(weight)), 
     se = diagis::weighted_se(x = qanon_by_person %>% pull(q_exposure_flag), 
     w = qanon_by_person %>% pull(weight))) %>% 
  mutate(low = mean - se * 1.96,
         high = mean + se * 1.96)
```

## Avg. exposures among the exposed

```{r}
tibble(mean = diagis::weighted_mean(x = qanon_by_person %>% filter(q_exposure_n > 0) %>% pull(q_exposure_n),
     w = qanon_by_person %>% filter(q_exposure_n > 0) %>%  pull(weight)), 
     se = diagis::weighted_se(x = qanon_by_person %>% filter(q_exposure_n > 0) %>% pull(q_exposure_n), 
     w = qanon_by_person %>% filter(q_exposure_n > 0) %>% pull(weight))) %>% 
  mutate(low = mean - se * 1.96,
         high = mean + se * 1.96)

reldist::wtd.quantile(x = qanon_by_person %>% filter(q_exposure_n > 0) %>% pull(q_exposure_n),
                      weight = qanon_by_person %>% filter(q_exposure_n > 0) %>%  pull(weight),
                      q = .5)

reldist::wtd.quantile(x = qanon_by_person %>% filter(q_exposure_n > 0) %>% pull(q_exposure_n),
                      weight = qanon_by_person %>% filter(q_exposure_n > 0) %>%  pull(weight),
                      q = .025)

reldist::wtd.quantile(x = qanon_by_person %>% filter(q_exposure_n > 0) %>% pull(q_exposure_n),
                      weight = qanon_by_person %>% filter(q_exposure_n > 0) %>%  pull(weight),
                      q = .975)
```
Trump supporters
```{r}
reldist::wtd.quantile(x = qanon_by_person %>% filter(q_exposure_n > 0 & presvote20combined == "Donald Trump") %>% pull(q_exposure_n),
                      weight = qanon_by_person %>% filter(q_exposure_n > 0) %>%  pull(weight),
                      q = .5)

reldist::wtd.quantile(x = qanon_by_person %>% filter(q_exposure_n > 0 & presvote20combined == "Donald Trump") %>% pull(q_exposure_n),
                      weight = qanon_by_person %>% filter(q_exposure_n > 0) %>%  pull(weight),
                      q = .025)

reldist::wtd.quantile(x = qanon_by_person %>% filter(q_exposure_n > 0 & presvote20combined == "Donald Trump") %>% pull(q_exposure_n),
                      weight = qanon_by_person %>% filter(q_exposure_n > 0) %>%  pull(weight),
                      q = .975)
```


Trump supporters
```{r}
reldist::wtd.quantile(x = qanon_by_person %>% filter(q_exposure_n > 0 & presvote20combined == "Joe Biden") %>% pull(q_exposure_n),
                      weight = qanon_by_person %>% filter(q_exposure_n > 0) %>%  pull(weight),
                      q = .5)

reldist::wtd.quantile(x = qanon_by_person %>% filter(q_exposure_n > 0 & presvote20combined == "Joe Biden") %>% pull(q_exposure_n),
                      weight = qanon_by_person %>% filter(q_exposure_n > 0) %>%  pull(weight),
                      q = .025)

reldist::wtd.quantile(x = qanon_by_person %>% filter(q_exposure_n > 0 & presvote20combined == "Joe Biden") %>% pull(q_exposure_n),
                      weight = qanon_by_person %>% filter(q_exposure_n > 0) %>%  pull(weight),
                      q = .975)
```


```{r}
plot_n <- qanon_by_person %>% 
  filter(q_exposure_flag == 1) %>% 
  ggplot(aes(q_exposure_n)) +
  geom_histogram(alpha = 1) +
  scale_fill_grey() +
  scale_x_log10() +
  labs(title = "Distribution of Total QAnon Website Visits",
       subtitles = "By presidential support",
       x = "log scale of # of QAnon website visits") +
  theme_classic() +
  theme(legend.position = "none")
```

```{r}
plot_per <- qanon_by_person %>% 
  filter(q_exposure_flag == 1) %>% 
  ggplot(aes(qanon_per)) +
  geom_histogram(alpha = 1) +
  scale_fill_grey() +
  scale_x_log10(labels = function(x) paste0(x*100, "%")) +
  labs(title = "Distribution of % of news diet that are QAnon websites",
       x = "log scale of the % of news diet that are QAnon websites") +
  theme_classic() +
  theme(legend.position = "none")
```

```{r}
ggpubr::ggarrange(plot_n, plot_per, ncol = 1, labels = c("A", "B"))
```



## Percent of news diet

Of everyone

```{r}
tibble(mean = diagis::weighted_mean(x = qanon_by_person %>% filter(!is.na(qanon_per)) %>% pull(qanon_per),
     w = qanon_by_person %>% filter(!is.na(qanon_per)) %>%  pull(weight)), 
     se = diagis::weighted_se(x = qanon_by_person %>% filter(!is.na(qanon_per)) %>% pull(qanon_per), 
     w = qanon_by_person %>% filter(!is.na(qanon_per)) %>% pull(weight))) %>% 
  mutate(low = mean - se * 1.96,
         high = mean + se * 1.96)
```

Of people who were exposed to QAnon websites

```{r}
tibble(mean = diagis::weighted_mean(x = qanon_by_person %>% filter(!is.na(qanon_per) & q_exposure_flag == 1) %>% pull(qanon_per),
     w = qanon_by_person %>% filter(!is.na(qanon_per) & q_exposure_flag == 1) %>%  pull(weight)), 
     se = diagis::weighted_se(x = qanon_by_person %>% filter(!is.na(qanon_per) & q_exposure_flag == 1) %>% pull(qanon_per), 
     w = qanon_by_person %>% filter(!is.na(qanon_per) & q_exposure_flag == 1) %>% pull(weight))) %>% 
  mutate(low = mean - se * 1.96,
         high = mean + se * 1.96)
```


## Avg. time on domain

Raw data for time duration calculations cannot be provided to preserve participant privacy.


## Exposure regression

```{r}
qanon_exposure_model <- lm(q_exposure_flag ~ trump_support + knowledge + interest + college + female + non_white + age4_30_44 + age4_45_64 + age4_65, data = qanon_by_person, weights = weight) 
```

```{r}
qanon_exposure_model %>% 
  summary()
```

```{r, results='asis'}
stargazer::stargazer(qanon_exposure_model, header = FALSE, type = "latex", dep.var.labels.include = F, dep.var.caption = "Exposure to at least one QAnon website (binary) ", model.numbers = F, covariate.labels = c("Trump supporter", "Political knowledge", "Political interest", "College", "Female", "Non-white", "Age 30-44 years", "Age 45-64 years", "Age 65+"), star.char = c("*", "**", "***"), star.cutoffs = c(0.05, 0.01, 0.001))
```


## age

```{r}
ages <- qanon_by_person %>% 
  group_by(age4) %>% 
  summarize(x = sum(q_exposure_flag * weight),
            n = sum(weight)) %>% 
  rowwise %>%
  mutate(tst = list(broom::tidy(prop.test(x, n, conf.level=0.95)))) %>%
  tidyr::unnest(tst)
```

```{r}
ages %>% 
  mutate(age4 = factor(age4, levels = c("Under 30", "30-44", "45-64", "65+"))) %>% 
  ggplot(aes(x = age4, ymin = conf.low, y = estimate, ymax = conf.high, color = age4))+
  geom_pointrange()+
  scale_color_grey()+
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, .025), limits = c(0,.11))+
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  labs(title = "Proportion Exposed to QAnon Websites by Age Group", 
       x = "",
       y = "% exposed to QAnon websites") +
  theme_bw()+
  theme(legend.position = "none", panel.grid.major.x = element_blank())
```

## media decile

```{r}
media_deciles <- qanon_by_person %>% 
  group_by(ideology_bin) %>% 
  summarize(x = sum(q_exposure_flag * weight),
            n = sum(weight)) %>% 
  rowwise %>%
  mutate(tst = list(broom::tidy(prop.test(x, n, conf.level=0.95)))) %>%
  tidyr::unnest(tst)
```

```{r}
media_deciles %>% 
  ggplot(aes(x = ideology_bin, ymin = conf.low, y = estimate, ymax = conf.high))+
  geom_pointrange() +
  #scale_color_grey() +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, .025), limits = c(0,.152)) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
 labs(x = "average media diet slant quantile
  (liberal to conservative)", 
       y = "% exposed to QAnon websites",
       title = "Proportion Exposed to QAnon Websites by Media Quantile") + 
  theme_bw()+
  theme(legend.position = "none", 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())
```

## presidential support

```{r}
pres_support <- qanon_by_person %>% 
  group_by(trump_support) %>% 
  summarize(x = sum(q_exposure_flag * weight),
            n = sum(weight)) %>% 
  rowwise %>%
  mutate(tst = list(broom::tidy(prop.test(x, n, conf.level=0.95)))) %>%
  tidyr::unnest(tst)
```

```{r}
prop.test(x = c(pres_support %>% filter(trump_support == 1) %>% pull(x),
                pres_support %>% filter(trump_support == 0) %>% pull(x)),
          n = c(pres_support %>% filter(trump_support == 1) %>% pull(n),
                pres_support %>% filter(trump_support == 0) %>% pull(n))) %>% 
  broom::tidy()
```


```{r}
pres_support %>% 
  ggplot(aes(x = trump_support, ymin = conf.low, y = estimate, ymax = conf.high))+
  geom_pointrange() +
  #scale_color_grey() +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, .025), limits = c(0,.152)) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
 labs(x = "0 = Non-Trump supporter, 1 = Trump supporter", 
       y = "% exposed to QAnon websites",
       title = "Proportion Exposed to QAnon Websites by Candidate Support") + 
  theme_bw()+
  theme(legend.position = "none", 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())
```

```{r}
ages_qanon <- qanon_by_person %>% 
  group_by(age4) %>% 
  summarize(x = sum(q_exposure_flag * weight),
            n = sum(weight)) %>% 
  rowwise %>%
  mutate(tst = list(broom::tidy(prop.test(x, n, conf.level=0.95)))) %>%
  tidyr::unnest(tst)
```

```{r}
age_plot_qanon <- ages_qanon %>% 
  mutate(age4 = factor(age4, levels = c("Under 30", "30-44", "45-64", "65+"))) %>% 
  ggplot(aes(x = age4, ymin = conf.low, y = estimate, ymax = conf.high, color = age4))+
  geom_pointrange()+
  scale_color_grey()+
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, .025), limits = c(0, .15))+
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  labs(title = "Age", 
       x = "",
       y = "") +
  theme_bw()+
  theme(legend.position = "none", panel.grid.major.x = element_blank())
```

## media decile

```{r}
media_deciles_qanon <- qanon_by_person %>% 
  group_by(ideology_bin) %>% 
  summarize(x = sum(q_exposure_flag * weight),
            n = sum(weight)) %>% 
  rowwise %>%
  mutate(tst = list(broom::tidy(prop.test(x, n, conf.level=0.95)))) %>%
  tidyr::unnest(tst)
```

```{r}
media_plot_qanon <- media_deciles_qanon %>% 
  ggplot(aes(x = ideology_bin, ymin = conf.low, y = estimate, ymax = conf.high))+
  geom_pointrange() +
  #scale_color_grey() +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, .025), limits = c(0, .16)) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
 labs(x = "", 
       y = "",
       title = "Media Diet Slant") + 
  theme_bw()+
  theme(legend.position = "none", 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())
```

```{r}
race_qanon <- qanon_by_person %>% 
  group_by(race4) %>% 
  summarize(x = sum(q_exposure_flag * weight),
            n = sum(weight)) %>% 
  rowwise %>%
  mutate(tst = list(broom::tidy(prop.test(x, n, conf.level=0.95)))) %>%
  tidyr::unnest(tst)
```

```{r}
race_plot_qanon <- race_qanon %>% 
  ggplot(aes(x = reorder(race4, desc(estimate)), ymin = conf.low, y = estimate, ymax = conf.high, color = reorder(race4, desc(estimate)))) +
  geom_pointrange() +
  #scale_color_grey() +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, .025), limits = c(0, .15))+
  scale_color_grey() +
 labs(x = "", 
       y = "",
       title = "Race") + 
  theme_bw()+
  theme(legend.position = "none", 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())
```

```{r fig.height=6, fig.width=6}
ggpubr::ggarrange(age_plot_qanon, race_plot_qanon, labels = c("A", "B"), ncol = 1) %>% 
   ggpubr::annotate_figure(top = ggpubr::text_grob("Proportion Exposed to QAnon Websites By:"))

```

# Intraindividual statistics

Raw data to calculate this statistic is not available because it requires raw data that we cannot share to protect participant privacy. 

# Time to cluster!

```{r}
cluster_data <- read_csv("data/cluster_data.csv")
```


```{r}
cluster_data_behaviors <- cluster_data %>% 
  select(ientropy, acf, mean, sd)
```

```{r}
cluster_data_behaviors %>% 
  summarize(entropy_mean = mean(ientropy),
            entropy_sd = sd(ientropy),
            acf_mean = mean(acf),
            acf_sd = sd(acf),
            mean_mean = mean(mean),
            mean_sd = sd(mean),
            sd_mean = mean(sd),
            sd_sd = sd(sd))
```

```{r}
squared_sums <- tibble()

for(i in 1:10){
  
  kmeans_output <- kmeans(cluster_data_behaviors, centers = i)
  
  squared_sums <- squared_sums %>% 
    rbind(tibble(k = i,
                 tot_withinss = kmeans_output$tot.withinss))
}
```

```{r}
squared_sums %>% 
  ggplot(aes(k, tot_withinss)) +
  scale_x_continuous(breaks = seq(1, 10, 1)) +
  geom_point() + 
  geom_line() +
  theme_bw()
```

```{r}
set.seed(6)
kmeans_output <- kmeans(cluster_data_behaviors, centers = 4)
```

```{r}
kmeans_output$centers %>% 
  as_tibble() %>% 
  filter(row_number() != 3) %>% 
  rownames_to_column() %>% 
  mutate_if(is.numeric, round, 2) %>% 
  cbind(cluster_name = c("Regular", "Diverse", "Selective")) %>% 
  select(rowname, cluster_name, ientropy, acf, mean, sd) %>% 
  knitr::kable(col.names = c("Cluster #", "Cluster Name", "entropy", "inertia (acf)", "daily mean", "daily sd"))
```

```{r}
clusters <- cluster_data %>% 
  cbind(cluster = as.factor(kmeans_output$cluster)) %>% 
  filter(cluster != 3) %>% 
  mutate(cluster = if_else(cluster == "4", as.character("3"), as.character(cluster)))
```

```{r}
multi_1 <- multinom(cluster ~ trump_support + knowledge + interest + college + female + non_white + age4_30_44 + age4_45_64 + age4_65, data = clusters, weights = weight) 
```

```{r}
multi_1 %>% 
  broom::tidy() %>% 
  mutate(significant = if_else(p.value <= .05, "1", "0"),
         odds_ratio = exp(estimate)) %>% 
  ggplot(aes(term, estimate, color = significant, shape = `y.level`)) +
  geom_point(size = 3) +
  coord_flip() +
  theme_bw()
```

```{r, results='asis'}
stargazer::stargazer(multi_1, 
                     type = "latex",
                     dep.var.caption = "Membership in cluster", 
                     model.numbers = F, 
                     covariate.labels = c("Trump supporter", "Political knowledge", "Political interest", "College", "Female", "Non-white", "Age 30-44 years", "Age 45-64 years", "Age 65+"), 
                     star.char = c("*", "**", "***"), 
                     star.cutoffs = c(0.05, 0.01, 0.001))
```

```{r}
qanon_by_person %>% 
  ungroup() %>% 
  slice_max(q_exposure_n, n =2)
```

```{r}
clusters %>% 
  filter(cluster == 3)
```

```{r}
clusters %>% 
  mutate(cluster = case_when(
    cluster == 1 ~ "1. Regular",
    cluster == 2 ~ "2. Diverse",
    cluster == 3 ~ "3. Selective"
  )) %>% 
  ggplot(aes(mean, ientropy,  fill = as.factor(cluster), color = as.factor(cluster))) +
  stat_ellipse(type = "t", geom = "polygon", alpha = 0.4, level = .90) +
  geom_point(size = 2) +
  scale_x_log10() +
  theme_classic() +
  labs(title = "K-means clustering results",
       subtitle = "each point = one person's behavioral metrics",
       x = "log scale of daily mean visits",
       y = "entropy",
       color = "cluster",
       fill = "cluster")
```


5 groups


```{r, results='asis'}
qanon_by_person %>% 
  mutate(quantile = ntile(mean_ideology, 5)) %>% 
  lm(q_exposure_flag ~ as.factor(quantile), data = ., weights = weight) %>% 
stargazer::stargazer(header = FALSE, type = "latex", dep.var.labels.include = F, dep.var.caption = "Exposure to at least one QAnon website", model.numbers = F, covariate.labels = c("Quantile 2", "Quantile 3", "Quantile 4", "Quantile 5"), star.char = c("*", "**", "***"), star.cutoffs = c(0.05, 0.01, 0.001), single.row = T)
```


